---
---

# Iterate with purrr

===

We already used stringr in the dplyr lesson to modify NAICS codes: `str_detect`, `str_c`, `str_remove`

Here we will manipulate the "term"" column of the `broom` output to improve figure axis labels. Load `stringr`

Load `stringr` as well as `dplyr`.

```{r}
library(stringr)
library(dplyr)
```

===

Use `dplyr`'s `pull` function to extract the column "term" from the tidyfit1 data frame. 
Remove the word "Sector" and modify to title case.

```{r title = "worksheet-1.R", message=FALSE}
tidyfit1 %>%
  pull(term) %>%
  str_remove("Sector") %>%
  str_to_title()
```

===

Another handy function in `stringr` truncates long strings

```{r}
tidyfit1 %>%
  pull(term) %>%
  str_remove("Sector") %>%
  str_to_title() %>%
  str_trunc(30, side = "right", ellipsis = "")
```

===

A core syntax element of the tidyverse is the **piped workflow** where the object on the left-hand side of `%>%` becomes the first argument to the function on the right-hand side. This reduces intermediate objects filling up your workspace and can improve readability. 

```{r title = "worksheet-1.R", message=FALSE}
term1 <- pull(tidyfit1, term)
term2 <- str_remove(term1, "Sector")
term3 <- str_to_title(term2)
```

or 

```{r}
str_to_title(str_remove(pull(tidyfit1, term), "Sector"))
```

===

Another core tidyverse method is to use `purrr`'s `map_` functions for iteration, instead of for loops, s/l/apply functions, or copy-paste. Here we use `map_chr` to create the new term vector within a mutate function. The `.` represents each item from the first argument to be iterated over and the `~` is an anonymous function. `map_chr` returns a character vector. 

```{r}
library(purrr)
tidyfit1 <- tidyfit1 %>%
  mutate(term = map_chr(term, 
          ~str_remove(., "Sector") %>% 
           str_to_title())) 
```

```{r title = "Console"}
tidyfit1$term
```

