---
---

# Tidy models

We will start with the Census data set that was generated in the prior lesson.

Recall that we were interested modeling the median income across counties. 

$$
median\_income \sim industry + establishment\_size
$$

===

Read in the `acs_cbp.csv` using the appropriate function in `readr`. 

```{r}
library(readr)
acs_cbp <- read_csv("data/acs_cbp.csv")
```

===

Create a simple model comparing median income across Sectors. 
One way to view details of the model fit is with `summary`. 

```{r}
fit1 <- glm(median_income ~ Sector, 
            family = gaussian, 
            data = acs_cbp)
summary(fit1)
```

===

The `broom` package helps to clean up the untidy structure of
model outputs such as what is returned from `lm`, `nls`, `t.test`. 

The `tidy` function creates a "tibble" with one row for each
important component of the model.

```{r}
library(broom)
tidy(fit1)
```

===

This may be useful for plotting, especially with the argument 
to include estimated confidence intervals to use with `ggplot2`'s
`geom_errobar`.

```{r}
tidyfit1 <- tidy(fit1, conf.int = TRUE)

library(ggplot2)

ggplot(tidyfit1, aes(x = term, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) + 
  theme_bw() +
  coord_flip()
```

===

Use `glance` to retrieve goodness of fit measures and related statistics
as one row per model. The metrics will depend on model type. 

```{r}
glance(fit1)
```

===

Use `augment` to add a column to a dataset containing information such as fitted values,
residuals, or cluster assignments. Column names have a `.` prefix to avoid overwriting
existing column names. The first argument is a model object and the 2nd is data

```{r warning=FALSE}
acs_cbp2 <- augment(fit1, data = acs_cbp)
names(acs_cbp2)
```

