---
---

# File manipulation

The `fs` package has functions for interacting with the file system.

===

We will copy some files from public-data for demonstration purposes.

```{r}
library(fs)
path <- "/nfs/public-data/NOAA/www.ncdc.noaa.gov"
```

===

Find files with matching patterns in this highly nested set of folders. 

```{r}
details <- dir_ls(path, 
                  recursive = TRUE, 
                  regexp = "details")
# locations <- dir_ls(path, recursive = TRUE, regexp = "locations")
# fatalities <- dir_ls(path, recursive = TRUE, regexp = "fatalities")
basename(details)
dirname(details)
```

===

Copy *just* files 57-59 into a new folder called "details" in your data folder.

```{r}
file_copy(path = details[57:59], 
          new_path = dir_create("data/details/"))
```

===

Read in files from new location and create one big data frame using `purrr`'s `map_df` to iterate the `read_csv` function over the file paths. `.id` is a column name to identify each of the file paths. 

```{r message=FALSE}
details_df <- dir_ls("data/details") %>% 
  map_df(read_csv, .id = "filename")

head(details_df)
```

