---
---

# File manipulation

The `fs` package has functions for interacting with the file system.

===

We will copy some files from public-data for demonstration purposes

```{r}
library(fs)
path <- "/nfs/public-data/NOAA/www.ncdc.noaa.gov"
```

===

Find files with matching patterns 

```{r}
details <- dir_ls(path, recursive = TRUE, regexp = "details")
# locations <- dir_ls(path, recursive = TRUE, regexp = "locations")
# fatalities <- dir_ls(path, recursive = TRUE, regexp = "fatalities")
```

===

Copy into new folders (maybe only copy the ones that work here?)

```{r}
file_copy(details, new_path = dir_create("data/details/")) # slow
```

===

Read in files from new location and create one big data frame.

`map_df` applies function to a list of elements and binds dfs together
assuming they can be combined. Read in *just* files 57-59. 

```{r message=FALSE}
details <- dir_ls("data/details")
basename(details)
```

```{r message=FALSE}
details_df <- details[57:59] %>% 
  map_df(read_csv, .id = "filename")
```

```{r}
head(details_df)
```

