---
---

# maps!

===

Do something else with forcats.. 
Make some categories for deadly and non-deadly storms, damages reported and not

```{r}
# fct_collapse() # to combine categories
```

===

make into a simple features object using lat and lon columns and put on leaflet map.
Notice `drop_na` from tidyr. 

```{r}
library(sf)

details_sf <- details_df %>%
  dplyr::select(BEGIN_LAT, BEGIN_LON, END_LAT, END_LON, DEATHS_DIRECT,
                EPISODE_NARRATIVE, EVENT_NARRATIVE, STATE, BEGIN_DATE_TIME) %>%
  tidyr::drop_na(BEGIN_LAT) %>%
  st_as_sf(coords = c("BEGIN_LON", "BEGIN_LAT"), crs = 4326) %>%
  dplyr::filter(DEATHS_DIRECT > 0)
```

===

`sf` objects can be plotted with `geom_sf`

```{r}
details_sf %>%
  ggplot() +
  geom_sf()
```

===

Make an interactive map with base layers using leaflet.

```{r}
library(leaflet)

details_sf %>%
  leaflet() %>%
  addTiles() %>%
  addMarkers()
```

===

Jazz it up a bit with pop-ups, clustering, and layers. 

```{r}
details_sf %>%
  leaflet() %>%
  addTiles() %>%
  addMarkers(popup = ~EPISODE_NARRATIVE, 
             clusterOptions = markerClusterOptions(),
             group = "episodes") %>%
  addLayersControl(overlayGroups = c("episodes"))
```