---
---

# Dates and times 

===

See an unambiguously formatted datetime with

```{r}
Sys.time()
```

===

What is it actually?

```{r}
as.numeric(Sys.time())
```

===

There are several columns in the storm events data with dates and times.

```{r}
names(details_df)
```

Unfortunately they are not in the desired format.

```{r}
details_df$BEGIN_DATE_TIME %>% head()
```


===

Use strptime or as.POSIXct to convert. For help specifying the format refer to [link]().

```{r}
details_df %>%
  mutate(begin_iso_date = as.POSIXct(BEGIN_DATE_TIME, 
                                     format = "%d-%b-%y %H:%M:%S")) %>%
  pull(begin_iso_date) %>% head(10)
```

===

lubridate has a slightly faster version of strptime

```{r}
library(lubridate)
fast_strptime(details_df$BEGIN_DATE_TIME, format = "%d-%b-%y %H:%M:%S")
```

===

Or if you don't want to look up the letter codes for strptime

```{r}
details_iso <- details_df %>% 
  mutate(begin_datetime_iso = dmy_hms(BEGIN_DATE_TIME),
         end_datetime_iso = dmy_hms(END_DATE_TIME)) 
```

===

Intervals, durations, and time periods are where `lubridate` shinys. 

Make a time interval using the `%--%` operator, then calculate its duration.

```{r}
details_iso %>%
  mutate(event_interval = begin_datetime_iso %--% end_datetime_iso,
         event_duration = as.duration(event_interval),
         event_duration_days = event_interval/days(1)) %>%
  dplyr::select(event_interval, event_duration, event_duration_days) %>% head() 
```

===

Timezones aren't correct though. See correctly formatted timezone names using OlsonNames().
We'll switch one to use correctly.

instead of using nested ifelse statements or switch, use case_when to modify the timezone column.
case_when is particularly good for creating new variables that rely on a complex combination of 
existing variables

```{r}
library(dplyr)
details_df <- details_df %>%
  mutate(tz_olson = case_when(
    CZ_TIMEZONE == "CST" ~ "US/Central")
  )

```

